opioid_crisis_code

### 2020-05-07 Opioid_Crisis_Code.Rmd
moved data to a folder

deathsbycommondiseases <- read_csv("deathsbycommondiseases.csv", 
                          col_types = "ldddddd") %>%
  select(Year, `Deaths by Cancer`, `Deaths by Drug Overdose`, 
         `Deaths by CVD`) %>%
  mutate(`Proportion of 1999 Deaths by Cancer` = 
           `Deaths by Cancer`/549829) %>%
  mutate(`Proportion of 1999 Deaths by Drugs` = 
           `Deaths by Drug Overdose`/19122) %>%
  mutate(`Proportion of 1999 Deaths by CVD` = 
           `Deaths by CVD`/949900)

@@

death_by_year_and_state <- read_csv("Drug Overdose Deaths by Year and State.csv"
, col_types = "lcdccddddc") %>%
  filter(`Crude Rate` != "Unreliable")

@@

treatment_locations <- read_csv("Drug Treatment Centers.csv", 
                                col_types = "ccccccccc") %>%
  select(`Program Name`, Street, City, State, Zipcode)

@@

state_pop <- read_csv("State Population Estimate.csv", col_types = "dccdcdddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddd") %>%
  rename(state_full = NAME) %>%
  mutate(state_full = tolower(state_full))

@@

longlatinfo <- read_csv("uscitieslonglat.csv", 
                        col_types = "ccccdcccddddcllcdcd") %>%
  rename(City = city) %>%
  rename(State = state_id)

@@

# not in final but map of distribution of treatment centers per capita

@@

mavsus_death <- read_csv("MAAgeAdjustedOpioidRelatedDeathRateByYear.csv", 
                         col_types = "cdc")

@@

counties <- read_csv("zip_codes_states.csv",
                     col_types = "dddccc") %>%
  filter(state == "MA") %>%
  rename(County = county) %>%
  rename(Municipality = city)

@@

madeathbycounty <- read_csv(
  "MAAverageAnnualOpioidRelatedDeathRateper100,000People.csv",
                            col_types = "cdcdddc")

@@

countypop <- read_csv("countypop.csv",
                      col_types = "cdd") %>%
  mutate(Pop = Pop/100000) %>%
  rename(subregion = CTYNAME) %>%
  mutate(subregion = tolower(subregion)) %>%
  select(subregion, Pop)

@@

povertybycounty <- read_csv("PovertyByCounty.csv",
                            col_types = "cd") %>%
  rename(subregion = County) %>%
  mutate(subregion = tolower(subregion))

@@

ageopioidmodel <- read_csv("U.S. age vs. opioid deaths.csv", 
                           col_types = "dcc") %>%
  clean_names() %>%
  filter(number_of_deaths != "N/A") %>%
  filter(age_range != "Total") %>%
  mutate(age_range = as.factor(age_range)) %>%
    mutate(number_of_deaths = as.numeric(number_of_deaths))

@@

raceopioidmodel <- read_csv("U.S. race vs. opioid deaths.csv", 
                            col_types = "dcc") %>%
  clean_names() %>%
  na.omit() %>%
  mutate(race = as.factor(race)) %>%
  mutate(opioid_deaths = as.numeric(opioid_deaths))

>>>>

deathsbycommondiseases <- read_csv("raw-data/deathsbycommondiseases.csv", 
                          col_types = "ldddddd") %>%
  select(Year, `Deaths by Cancer`, `Deaths by Drug Overdose`, 
         `Deaths by CVD`) %>%
  mutate(`Proportion of 1999 Deaths by Cancer` = 
           `Deaths by Cancer`/549829) %>%
  mutate(`Proportion of 1999 Deaths by Drugs` = 
           `Deaths by Drug Overdose`/19122) %>%
  mutate(`Proportion of 1999 Deaths by CVD` = 
           `Deaths by CVD`/949900)

@@

death_by_year_and_state <- read_csv("raw-data/Drug Overdose Deaths by Year and State.csv"
, col_types = "lcdccddddc") %>%
  filter(`Crude Rate` != "Unreliable")

@@

treatment_locations <- read_csv("raw-data/Drug Treatment Centers.csv", 
                                col_types = "ccccccccc") %>%
  select(`Program Name`, Street, City, State, Zipcode)

@@

state_pop <- read_csv("raw-data/State Population Estimate.csv", col_types = "dccdcdddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddd") %>%
  rename(state_full = NAME) %>%
  mutate(state_full = tolower(state_full))

@@

longlatinfo <- read_csv("raw-data/uscitieslonglat.csv", 
                        col_types = "ccccdcccddddcllcdcd") %>%
  rename(City = city) %>%
  rename(State = state_id)

@@

# map of distribution of treatment centers per capita

@@

mavsus_death <- read_csv("raw-data/MAAgeAdjustedOpioidRelatedDeathRateByYear.csv", 
                         col_types = "cdc")

@@

counties <- read_csv("raw-data/zip_codes_states.csv",
                     col_types = "dddccc") %>%
  filter(state == "MA") %>%
  rename(County = county) %>%
  rename(Municipality = city)

@@

madeathbycounty <- read_csv(
  "raw-data/MAAverageAnnualOpioidRelatedDeathRateper100,000People.csv",
                            col_types = "cdcdddc")

@@

countypop <- read_csv("raw-data/countypop.csv",
                      col_types = "cdd") %>%
  mutate(Pop = Pop/100000) %>%
  rename(subregion = CTYNAME) %>%
  mutate(subregion = tolower(subregion)) %>%
  select(subregion, Pop)

@@

povertybycounty <- read_csv("raw-data/PovertyByCounty.csv",
                            col_types = "cd") %>%
  rename(subregion = County) %>%
  mutate(subregion = tolower(subregion))

@@

ageopioidmodel <- read_csv("raw-data/U.S. age vs. opioid deaths.csv", 
                           col_types = "dcc") %>%
  clean_names() %>%
  filter(number_of_deaths != "N/A") %>%
  filter(age_range != "Total") %>%
  mutate(age_range = as.factor(age_range)) %>%
    mutate(number_of_deaths = as.numeric(number_of_deaths))

@@

raceopioidmodel <- read_csv("raw-data/U.S. race vs. opioid deaths.csv", 
                            col_types = "dcc") %>%
  clean_names() %>%
  na.omit() %>%
  mutate(race = as.factor(race)) %>%
  mutate(opioid_deaths = as.numeric(opioid_deaths))
